On Secure Delegation of SampBQP with a Classical Client

### 2019-11-23 hamiltonian.tex
Rename Hamiltonian and ground state label

\begin{theorem}
	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{circuit}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{circuit}}=0\Rightarrow\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}
	We ensure states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	\begin{corollary}
		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$
	\end{corollary}

We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
\begin{align*}
	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{circuit}|y}=0}
\end{align*}
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}

>>>>

\begin{theorem}
	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{C(x)}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item $H_{C(x)}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}
	We ensure states perpendicular to $\ket{\psi_{C(x)}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	\begin{corollary}
		$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{C(x)}}}$
	\end{corollary}

We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{C(x)}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
\begin{align*}
	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{\psi_{C(x)}|y}=0}
\end{align*}
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{C(x)}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}
